\documentclass[letterpaper,10pt]{article}

\usepackage[T1]{fontenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdfpagemode=FullScreen,
}


% Font options
\usepackage[sfdefault]{roboto}  % Sans-serif font

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{\Large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]

% Ensure PDF is machine readable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-7pt}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingList}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\setlength{\footskip}{5pt}

\begin{document}

\begin{center}
  \textbf{\Huge Diego Rezende Santos de Moura} \\
  \small \href{https://diegorezm.netlify.app/}{diegorezm.app} $|$ \href{mailto:diegommrez12@gmail.com}{diegommrez12@gmail.com} $|$ 
  \href{https://linkedin.com/in/diegorezm}{linkedin.com/diegorezm} $|$
  \href{https://github.com/diegorezm}{github/diegorezm}
\end{center}

\section*{Objective}
Full Stack Developer seeking opportunities to grow professionally and apply my knowledge. I focus on Java for backend and TypeScript for frontend with experience in Spring Boot and Nextjs frameworks.

\section{Technical Skills}
\resumeSubHeadingList
  \resumeItem{\textbf{Programming Languages}: Java, Javascript, Python}
  \resumeItem{\textbf{Frameworks}: Spring Boot, Nextjs}
    \resumeItem{\textbf{Databases}: PostgreSQL, MySQL, SQLite, MongoDB}
  \resumeItem{\textbf{Libraries \& Tools}: Git, Docker, Node, React, Svelte, Tailwind}
  \resumeItem{\textbf{Markup}: Html, Css, Markdown}
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingList
  \resumeSubheading
      {Convenience Store}{\href{https://github.com/diegorezm/convenience.store.api}{github}} 
      {Fullstack Web Application}{Spring Boot, Next.js, Docker, SQL}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Backend developed with Spring Boot, integrating an SQL database.}
          \resumeItem{\textbullet\ Implementation of CRUD (Create, Read, Update, Delete) operations for user interaction with the database, ensuring efficiency and security in access.}
          \resumeItem{\textbullet\ Robust authentication using Spring Security, ensuring user data protection.}
          \resumeItem{\textbullet\ Automated testing with JUnit and MockMvc to ensure application quality and stability.}
          \resumeItem{\textbullet\ Full containerization with Docker, simplifying the deployment process and increasing application portability.}
          \resumeItem{\textbullet\ Continuous integration and continuous delivery (CI/CD) set up with GitHub Actions, with Docker images hosted on Docker Hub, ensuring an agile and efficient development workflow.}
          \resumeItem{\textbullet\ Frontend developed with Next.js, TypeScript, and Tailwind, providing a dynamic and responsive user interface.}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingList
  \resumeSubheading
      {Soldier}{Mar 2022 -- Jan 2023}
      {Brazilian Army}{Pindamonhangaba, SP}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Responsible for armed guard duty, ensuring the security and integrity of military facilities.}
          \resumeItem{\textbullet\ Developed teamwork skills, effectively collaborating with fellow soldiers to accomplish missions and daily tasks.}
          \resumeItem{\textbullet\ Managed the entrance gate, including strict control of people entering and exiting, ensuring security and access control.}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd
\section{Education}
\resumeSubHeadingList
  \resumeSubheading
      {UNITAU}{Taubaté, SP, Brazil}
      {Analysis and Systems Development} {Jan 2023 -- Dec 2025}
\resumeSubHeadingListEnd

\section{Certifications}
\resumeSubHeadingList
    \resumeItem{\textbullet\ \normalsize{\href{https://cert.efset.org/KdGLiQ}{English proficiency certificate from EF SET}}}
    \resumeItem{\textbullet\ \normalsize{\href{https://udemy-certificate.s3.amazonaws.com/image/UC-6fc7d4af-701d-446a-b69b-8e167018a749.jpg?v=1706800581000}{JavaScript and TypeScript from basic to advanced course}}}
    \resumeItem{\textbullet\ \normalsize{\href{https://udemy-certificate.s3.amazonaws.com/image/UC-7074fe91-0541-4bfd-bc58-af41912a6361.jpg?v=1703254492000}{Data Structures and Algorithms course}}}
    \resumeItem{\textbullet\ \normalsize{\href{https://www.cursoemvideo.com/validacao-de-certificado/?codigo=798CE-654D-9}{Excel [40 Hours]}}}
\resumeSubHeadingListEnd

\end{document}
